PANCHANGE_data_preprocessing

### 2020-12-04 PANCHANGE_data_preprocessing2020-07-15.Rmd

## GLAD and EDGI
### Create data frame 
```{r GLAD and EDGI combined}
if(GLAD_and_EDGI == TRUE)
glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
```

>>>>

## GLAD and EDGI
### Create data frame
```{r GLAD and EDGI combined}
if(GLAD_and_EDGI == TRUE){
glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
}
```
